Self Regulation Ontology Retest Analyses

### 2018-08-08 code/SRO_Retest_Analyses.Rmd
added boot figure with task info for both

@@

Task level summary of bootstrapped reliabilities.

```{r message=FALSE, warning=FALSE}

p6_t <- arrangeGrob(p4_t, p5_t,nrow=1)

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 100)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Poster_Plot_t.jpg')
```

```{r echo=FALSE}
rm(p4_t, p5_t, p6_t)
```

>>>>

Both task level boot plots with trial info together

```{r}
boot_both_w_trial = arrangeGrob(boot_task_plot, boot_survey_plot, nrow=1)

ggsave('Boot_Both_w_trialinfo.jpg', plot = boot_both_w_trial, device = "jpeg", path = "../output/figures/", width = 38, height = 48, units = "in", limitsize = FALSE, dpi = 100)
```

@@
